Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2020-12-09 paper/dcpo_gender_roles.Rmd
clean up

To avoid any potential multidimensionality in the Public Gender Egalitarianism data, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE index.
The complete list of gender egalitarianism items is included in the Appendix.]
Thus, the "Public" in the name of the dataset does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.
We describe these source data in detail in the next section.

# The Source Data on Public Gender Egalitarianism

>>>>

To avoid any potential multidimensionality in the Public Gender Egalitarianism data, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as the `tradroles` questions, "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE source data.
The complete list of gender egalitarianism items is included in the Appendix.]
Thus, the "Public" in the name of the dataset does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.
We describe these source data in detail in the next section.

# Examining the Source Data on Public Gender Egalitarianism
